The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-10-29 paper/ms.tex
fixed some typos

\begin{abstract}
We present results of radiative transfer calculations to measure
the impact of gas bulk rotation on the morphology of the Lyman
$\alpha$ line in galaxies. We model a galaxy as a sphere with an
homogeneous mixture of dust and hydrogen at a constant
temperature. These spheres have a solid-body rotation with
maximum velocities in the range $0-300$ \kms and neutral
hydrogen optical depths in the range $\tau_{\rm
H}=10^{5}-10^{7}$. We also consider two kinds of spatial
distribution for the radiation sources with respect to the sphere:
central and homogeneous. We find that the line width and the intensity
at the line's center increase with rotational velocity. In the case of homogeneously distributed
sources, for large rotational velocities the line transforms from a
double peak to a single peak a the line center. Under the same
conditions the escape fraction increases $\sim 30\%$. For
radiation sources located off-center, the line morphology presents a
range of single, double and triple peaked lines. We show how these results are
useful to interpret recent spectroscopic results of distant $z\sim 2-3$ star
forming galaxies.
\end{abstract}

>>>>

\begin{abstract}
We present results of radiative transfer calculations to measure
the impact of gas bulk rotation on the morphology of the Lyman
$\alpha$ line in galaxies. We model a galaxy as a sphere with a
homogeneous mixture of dust and hydrogen at a constant
temperature. These spheres have a solid-body rotation with
maximum velocities in the range $0-300$ \kms and neutral
hydrogen optical depths in the range $\tau_{\rm
H}=10^{5}-10^{7}$. We also consider two kinds of spatial
distribution for the radiation sources with respect to the sphere:
central and homogeneous. We find that the line width and the intensity
at the line's centre increases with rotational velocity. In the case of homogeneously distributed
sources, for large rotational velocities the line transforms from a
double peak to a single peak at the line center. Under the same
conditions the escape fraction increases $\sim 30\%$. For
radiation sources located off-centre, the line morphology presents a
range of single, double and triple peaked lines. We show how these results are
useful to interpret recent spectroscopic results of distant $z\sim 2-3$ star
forming galaxies.
\end{abstract}
